Does the leaf economic spectrum hold within plant functional types? A Bayesian multivariate trait meta-analysis

### 2019-11-26 shiklomanov_formatted.tex
Final submission revisions

\input{authors.tex}
\date{}

@@

For each model fit, we ran independent five chains, continuing sampling until the final result achieved convergence as determined by a univariate Gelman-Rubin potential scale reduction statistic less than 1.1 for all parameters \citep{gelman_1992_inference}.
We implemented this sampling algorithm in a publicly available R \citep{team_2018_r} package (<http://github.com/ashiklom/mvtraits>).

@@

\bibliography{library}

\section{Tables}

@@

@@

\caption{\label{tab:}\label{tab:pfts}Names, labels, species counts, and number of non-missing observations of each trait for plant functional types (PFTs) used in this analysis.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{ccccccccccccccc}
\toprule
\multicolumn{5}{c}{ } & \multicolumn{5}{c}{Mass} & \multicolumn{5}{c}{Area} \\
\cmidrule(l{3pt}r{3pt}){6-10} \cmidrule(l{3pt}r{3pt}){11-15}
Label & PFT & Species & Leaf lifespan & SLA & N & P & Rd & Vcmax & Jmax & N & P & Rd & Vcmax & Jmax\\
\midrule
BlETr & Broadleaf Evergreen Tropical Tree & 1229 & 153 & 11710 & 7547 & 2912 & 237 & 205 & 58 & 4023 & 1684 & 326 & 225 & 152\\
BlETe & Broadleaf Evergreen Temperate Tree & 363 & 135 & 2210 & 1811 & 1194 & 121 & 36 & 16 & 928 & 339 & 196 & 106 & 87\\
BlDTr & Broadleaf Deciduous Tropical Tree & 286 & 82 & 2166 & 1545 & 812 & 98 & 54 & 30 & 813 & 500 & 113 & 56 & 53\\
BlDTe & Broadleaf Deciduous Temperate Tree & 345 & 181 & 9536 & 5982 & 2163 & 942 & 245 & 576 & 2163 & 398 & 866 & 697 & 849\\
BlDBo & Broadleaf Deciduous Boreal Tree & 62 & 58 & 908 & 898 & 340 & 142 & 0 & 0 & 141 & 60 & 11 & 5 & 5\\
\addlinespace
NlETe & Needleleaf Evergreen Temperate Tree & 130 & 66 & 2958 & 4940 & 3729 & 262 & 92 & 91 & 1227 & 462 & 84 & 274 & 106\\
NlEBo & Needleleaf Evergreen Boreal Tree & 30 & 24 & 530 & 1457 & 393 & 493 & 0 & 0 & 101 & 14 & 16 & 3 & 3\\
NlD & Needleleaf Deciduous Tree & 19 & 16 & 195 & 328 & 179 & 34 & 1 & 0 & 48 & 10 & 3 & 4 & 0\\
ShE & Shrub Evergreen & 1120 & 298 & 5018 & 3555 & 2404 & 207 & 22 & 13 & 1376 & 747 & 205 & 41 & 32\\
ShDTe & Shrub Deciduous Temperate & 330 & 100 & 3026 & 1525 & 1227 & 10 & 9 & 1 & 576 & 281 & 13 & 33 & 19\\
\addlinespace
ShDBo & Shrub Deciduous Boreal & 94 & 80 & 482 & 552 & 313 & 0 & 1 & 1 & 133 & 51 & 0 & 1 & 1\\
C3GAr & C3 Grass Arctic & 157 & 65 & 989 & 996 & 573 & 11 & 1 & 2 & 219 & 85 & 7 & 1 & 2\\
C3GTe & C3 Grass Temperate & 624 & 76 & 6322 & 3802 & 1541 & 103 & 21 & 27 & 1257 & 382 & 93 & 52 & 47\\
C4G & C4 Grass & 255 & 31 & 1312 & 1461 & 335 & 44 & 0 & 0 & 410 & 56 & 28 & 0 & 0\\
\bottomrule
\end{tabular}}
\end{table}

\section{Figures}

@@

@@

\noindent
\textbf{Data accessibility:}
The R code and ancillary data for running these analyses is publicly available online via the Open Science Framework at https://osf.io/w8y73/.
The TRY data request used for this analysis has been archived at http://try-db.org,
and can be retrieved by providing the TRY data request ID (\#1584).
Alternatively, the exact pre-formatted data used in this analysis are available on request to Alexey Shiklomanov (alexey.shiklomanov@pnnl.gov).

>>>>

\usepackage[noblocks]{authblk}

\author[1,*]{Alexey N. Shiklomanov <alexey.shiklomanov@pnnl.gov>}
\affil[1]{Joint Global Change Research Institute, Pacific Northwest National Laboratory, College Park, MD}

\author[2]{Elizabeth M. Cowdery <ecowdery@bu.edu>}
\affil[2]{Department of Earth \& Environment, Boston University, Boston, MA}

\author[3]{Michael Bahn <Michael.Bahn@uibk.ac.at>}
\affil[3]{Institute of Ecology, University of Innsbruck, 6020 Innsbruck, Austria}

\author[4]{Chaeho Byun <chaeho.byun@mail.mcgill.ca>}
\affil[4]{School of Civil and Environmental Engineering, Yonsei University, Seoul 03722, Korea}

\author[5]{Steven Jansen <steven.jansen@uni-ulm.de>}
\affil[5]{Institute of Systematic Botany and Ecology, Ulm University, Albert-Einstein-Allee 11, 89081, Ulm, Germany}

\author[6]{Koen Kramer <koen.kramer@wur.nl>}
\affil[6]{Department of Vegetation, Forest, and Landscape Ecology, Wageningen Environmental Research and Wageningen University, Wageningen, Gelderland, The Netherlands}

\author[7,8]{Vanessa Minden <vanessa.minden@uni-oldenburg.de>}
\affil[7]{Institute for Biology and Environmental Sciences, Carl von Ossietzky-University of Oldenburg, Carl von Ossietzky Str. 9-11, 26129 Oldenburg, Germany}
\affil[8]{Department of Biology, Ecology and Evolution, Vrije Universiteit Brussel, Pleinlaan 2, 1050 Brussels}

\author[9]{\"Ulo Niinemets <ylo.niinemets@emu.ee>}
\affil[9]{Institute of Agricultural and Environmental Sciences, Estonian University of Life Sciences, Kreutzwaldi 1, 51014 Tartu, Estonia}

\author[10]{Yusuke Onoda <yusuke.onoda@gmail.com>}
\affil[10]{Graduate School of Agriculture, Kyoto University, Kyoto, 605-8503, Japan}

\author[11]{Nadejda A. Soudzilovskaia <n.a.soudzilovskaia@cml.leidenuniv.nl>}
\affil[11]{Conservation Biology Department, Institute of Environmental Sciences, Leiden University, Leiden, The Netherlands}

\author[2]{Michael C. Dietze <dietze@bu.edu>}

\affil[*]{Corresponding author; Phone: (301) 314-6713; Fax: (301) 314-6719; Email: alexey.shiklomanov@pnnl.gov; Mail: 5825 University Research Ct., Office 3533, College Park, MD 20740}

\renewcommand\Authfont{\footnotesize}
\renewcommand\Affilfont{\scriptsize}
\date{}

@@

For each model fit, we ran independent five chains, continuing sampling until the final result achieved convergence as determined by a univariate Gelman-Rubin potential scale reduction statistic less than 1.1 for all parameters \citep{gelman_1992_inference}.
We implemented this sampling algorithm in a publicly available R \citep{r_361} package (http://github.com/ashiklom/mvtraits).

@@

\bibliography{bibliography}

\vspace{5mm}

\noindent
\textbf{Data accessibility:}
R code and data are available from the Open Science Framework: https://osf.io/w8y73/.
Trait data are archived in the TRY Plant Trait Database at http://try-db.org and can be retrieved by providing TRY data request ID \#1584.

\vspace{5mm}

@@

\section*{Tables}

@@

\caption{\label{tab:pfts} Names, labels, species counts, and number of non-missing observations of each trait for plant functional types (PFTs) used in this analysis.}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{ccccccccccccccc}
\toprule
\multicolumn{5}{c}{ } & \multicolumn{5}{c}{Mass} & \multicolumn{5}{c}{Area} \\
\cmidrule(l{3pt}r{3pt}){6-10} \cmidrule(l{3pt}r{3pt}){11-15}
Label & PFT & Species & Leaf lifespan & SLA & N & P & Rd & Vcmax & Jmax & N & P & Rd & Vcmax & Jmax\\
\midrule
BlETr & Broadleaf Evergreen Tropical Tree & 1229 & 153 & 11710 & 7547 & 2912 & 237 & 205 & 58 & 4023 & 1684 & 326 & 225 & 152\\
BlETe & Broadleaf Evergreen Temperate Tree & 363 & 135 & 2210 & 1811 & 1194 & 121 & 36 & 16 & 928 & 339 & 196 & 106 & 87\\
BlDTr & Broadleaf Deciduous Tropical Tree & 286 & 82 & 2166 & 1545 & 812 & 98 & 54 & 30 & 813 & 500 & 113 & 56 & 53\\
BlDTe & Broadleaf Deciduous Temperate Tree & 345 & 181 & 9536 & 5982 & 2163 & 942 & 245 & 576 & 2163 & 398 & 866 & 697 & 849\\
BlDBo & Broadleaf Deciduous Boreal Tree & 62 & 58 & 908 & 898 & 340 & 142 & 0 & 0 & 141 & 60 & 11 & 5 & 5\\
\addlinespace
NlETe & Needleleaf Evergreen Temperate Tree & 130 & 66 & 2958 & 4940 & 3729 & 262 & 92 & 91 & 1227 & 462 & 84 & 274 & 106\\
NlEBo & Needleleaf Evergreen Boreal Tree & 30 & 24 & 530 & 1457 & 393 & 493 & 0 & 0 & 101 & 14 & 16 & 3 & 3\\
NlD & Needleleaf Deciduous Tree & 19 & 16 & 195 & 328 & 179 & 34 & 1 & 0 & 48 & 10 & 3 & 4 & 0\\
ShE & Shrub Evergreen & 1120 & 298 & 5018 & 3555 & 2404 & 207 & 22 & 13 & 1376 & 747 & 205 & 41 & 32\\
ShDTe & Shrub Deciduous Temperate & 330 & 100 & 3026 & 1525 & 1227 & 10 & 9 & 1 & 576 & 281 & 13 & 33 & 19\\
\addlinespace
ShDBo & Shrub Deciduous Boreal & 94 & 80 & 482 & 552 & 313 & 0 & 1 & 1 & 133 & 51 & 0 & 1 & 1\\
C3GAr & C3 Grass Arctic & 157 & 65 & 989 & 996 & 573 & 11 & 1 & 2 & 219 & 85 & 7 & 1 & 2\\
C3GTe & C3 Grass Temperate & 624 & 76 & 6322 & 3802 & 1541 & 103 & 21 & 27 & 1257 & 382 & 93 & 52 & 47\\
C4G & C4 Grass & 255 & 31 & 1312 & 1461 & 335 & 44 & 0 & 0 & 410 & 56 & 28 & 0 & 0\\
\bottomrule
\end{tabular}}
\end{table}

@@

\section*{Figures}

@@
